%-------------------------
% Dynamic Template: LocalHire Agent
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.8in}

\urlstyle{same}
\setlength{\tabcolsep}{0in}
\raggedbottom
\raggedright

\titleformat{\section}{
  \vspace{6pt}\scshape\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{#2} \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{center}
    {\Huge \scshape Chandra Rup Daka } \\[4pt]
    \small
    \underline{+1 253-632-3181} ~
    \href{mailto:chandrarupdaka@gmail.com}{\underline{chandrarupdaka@gmail.com}} ~
    \href{https://https://www.linkedin.com/in/chandra-rup-daka/}{\underline{https://www.linkedin.com/in/chandra-rup-daka/}} ~
    \href{https://https://github.com/chandrarup}{\underline{https://github.com/chandrarup}}
\end{center}
\vspace{-6mm}

%----------SUMMARY----------
\vspace{-4mm}
\section{Professional Summary}
Generative AI Engineer with 2+ years of experience designing and deploying production-grade LLM and agentic solutions across enterprise environments. Skilled in NLP, Deep Learning, and Retrieval-Augmented Generation (RAG) systems, with a proven track record of delivering intelligent systems at scale.
\vspace{-7mm}

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart

    \resumeSubheading
    {University of Houston}{Expected 2027}
    {M.S. in Engineering Data Science and Artificial Intelligence}{}
    \vspace{-2mm}

    \resumeSubheading
    {Amrita Vishwa Vidyapeetham}{2023}
    {B.Tech in Computer Science and Engineering (Specialization in Artificial Intelligence)}{}
    \vspace{-2mm}

\resumeSubHeadingListEnd
\vspace{-5mm}

%----------EXPERIENCE----------
\section{Experience}
\vspace{-1mm}
\resumeSubHeadingListStart

    \resumeSubheading{Accenture (GenWizard Platform)}{August 2023 - August 2025}{Advanced App Engineering Analyst - GenAI Specialist}{Architected production-grade LLM solutions for reverse engineering SDLC workflows. Achieved 89\% coverage in Technical Analysis with 9\% efficiency improvement. Designed custom RAG pipelines using LangChain and AutoGen. Mentored 30+ engineers. Recognized with Wall of Fame Award (Q4 FY24) and Client Recognition Award.}

    \resumeSubheading{Amrita Vishwa Vidyapeetham}{January 2023 - May 2023}{Undergraduate Research Assistant}{Developed deep learning framework for deepfake video detection achieving 96\% accuracy. Published in GCAT 2024. Conducted comprehensive literature review on AI-generated media forensics.}

    \resumeSubheading{Accenture}{January 2024 - August 2025}{Technical Mentor and Trainer}{Conducted training sessions on Python, agentic AI frameworks (LangChain, AutoGen, CrewAI), and GenAI best practices for 30+ junior engineers. Developed structured curriculum and provided hands-on mentorship.}

\resumeSubHeadingListEnd
\vspace{-5mm}

%-----------PROJECTS-----------
\vspace{-3mm}
\section{Projects}
\resumeSubHeadingListStart
\vspace{-2mm}

    \resumeProjectHeading{\textbf{Detection of Real and Manipulated Videos using Transfer Learning} | \emph{Python, TensorFlow, ResNet, XceptionNet, VGG16, LSTM, Bi-LSTM}}{}
    \resumeItemListStart
        \resumeItem{Developed deep learning framework for deepfake detection achieving 96\% accuracy on 6,500-video dataset. Published in GCAT October 2024.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Indian Sign Language Generation from Live Audio/Text (Tamil)} | \emph{Python, NLP, Computer Vision, BiLSTM, Transformers, Google Translate API}}{}
    \resumeItemListStart
        \resumeItem{Real-time speech-to-sign translation system for Tamil-speaking hearing-impaired community. Published in ICACCS March 2023.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Multi-Agent Deep Reinforcement Learning for Highway Merging} | \emph{Python, Keras, DQN, DDQN, CNN, Multi-Agent RL}}{}
    \resumeItemListStart
        \resumeItem{Autonomous vehicle on-ramp merging solution using DQN/DDQN with CNN-based policy network, Experience Replay buffers, and complex reward function balancing safety and efficiency.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Stock Price Prediction Using Deep Q-Learning} | \emph{Python, Deep Reinforcement Learning, DQN, TensorFlow}}{}
    \resumeItemListStart
        \resumeItem{Automated trading system learning optimal policies (Buy, Sell, Hold) using DQN with Experience Replay and dual-network architecture. Tested on Adani Enterprises stock data.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Speech Emotion Recognition System} | \emph{Python, CNN, librosa, RAVDESS Dataset}}{}
    \resumeItemListStart
        \resumeItem{CNN-based emotion recognition achieving 81.11\% accuracy. Implemented acoustic feature extraction (MFCCs, chroma, mel-spectrograms, tonnetz).}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Telugu News Article Classification} | \emph{Python, Word2Vec, LSTM, RNN, Bi-LSTM, NLP}}{}
    \resumeItemListStart
        \resumeItem{Low-resource NLP solution with custom Word2Vec embeddings for Telugu corpus. Achieved 82\% accuracy with Bi-LSTM model.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Social Distance Monitoring System} | \emph{Python, YOLOv3, OpenCV, COCO Dataset}}{}
    \resumeItemListStart
        \resumeItem{Real-time social distance violation detection using YOLOv3 with Euclidean distance computation and automated CCTV monitoring pipeline.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Hand Gesture Controlled Robotic Arm} | \emph{Arduino, Bluetooth (HC-05), Flex Sensors, MPU6050, PCA9685}}{}
    \resumeItemListStart
        \resumeItem{Gesture-based human-machine interface with Master-Slave control system. Wireless robotic arm control using natural hand movements.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Handwritten Character Recognition using HMM} | \emph{Python, Hidden Markov Models, Viterbi Algorithm, Computer Vision}}{}
    \resumeItemListStart
        \resumeItem{Machine learning model translating scanned handwritten documents to digital text. Achieved 99.9\% accuracy using Viterbi algorithm.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Real-Time Ball Tracking and Trajectory Analysis} | \emph{Python, OpenCV, Computer Vision, Deque}}{}
    \resumeItemListStart
        \resumeItem{Automated object tracking for sports analytics with HSV color space conversion. Achieved 32+ FPS with 3D trajectory visualization.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Number Writing Robotic Manipulator} | \emph{Python, ROS, MoveIt!, URDF, RViz}}{}
    \resumeItemListStart
        \resumeItem{Robotic manipulator performing precision writing tasks using ROS and MoveIt! framework with custom URDF model.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Operating Systems Chat Room Application} | \emph{C, IPC, Semaphores, Multithreading, Shared Memory}}{}
    \resumeItemListStart
        \resumeItem{Real-time messaging application implementing OS concepts: IPC, process synchronization, and mutex locks for race condition prevention.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProjectHeading{\textbf{Predictive Text Generator using Markov Chains} | \emph{Python, Markov Chains, NLP, Probability Models}}{}
    \resumeItemListStart
        \resumeItem{Predictive text application using Markov Chain theory for stochastic text generation. Evaluated trade-offs with LSTM-based approaches.}
    \resumeItemListEnd
    \vspace{-2mm}

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\vspace{-5mm}
\section{Skills}
\vspace{-2pt}
\small
\textbf{Languages:} Python, SQL, Java, C++, C \\[3pt]
\vspace{-0.5mm}
\textbf{Tools:} Docker, Git, ROS, OpenCV, Arduino IDE, Jupyter, VS Code, MoveIt!, RViz, Gazebo \\[3pt]
\vspace{-0.5mm}
\textbf{Frameworks:} TensorFlow, PyTorch, Keras, LangChain, AutoGen, CrewAI, FastAPI, Flask, Hugging Face Transformers, Scikit-learn

\end{document}